Probability Distribution Checks

### 2017-07-31 Probability_distribution_checks.Rmd
Correct errors in munging 2015 data
Correct days for AUDPS calculation in 2015

@@

car::qqp(AUDPS15$TShB_inc_AUDPS, "norm")
```

```{r 2015_TShB_inc_exp, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(AUDPS15$TShB_inc_AUDPS, "exp")
plot(f1)
car::qqp(AUDPS15$TShB_inc_AUDPS, "exp")
```

@@

These data do not fit this distribution, all values must be positive.

>>>>

## 2015

@@

car::qqp(AUDPS15$TShB_inc_AUDPS, "norm")

```

#### Tiller Incidence Log Normal

```{r 2015_TShB_inc_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$TShB_inc_AUDPS, "lnorm")
plot(f1)

car::qqp(AUDPS15$TShB_inc_AUDPS, "lnorm")
```

@@

These data do not fit this distribution, all values must be positive. There are
negative AUDPS values present.
